Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-11 docs/google-research-awards-latam/main.tex

    Affiliation: Federal University of Pernambuco, Department of
    Computer Science.\\

    Contacts at Google:~\Fix{...}

@@

Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
follow the constant changes in the language
specification~\cite{kangax}. In fact, recently, the JavaScript
specification went through a bigger change compared to prior
releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
the specification often demand sensible changes in implementations
that could lead to errors, including regressions. In fact, bugs in JS
implementations are often reported by the general public, some of
which were reported by our team.

>>>>

    Affiliation: Federal University of Pernambuco, Department of
    Computer Science\\

    Contact at Google:~Martin Barbella (mbarbella@google.com)

@@

Engine implementations (\eg{}, Google's V8\Fix{cite}, Mozilla's
SpiderMonkey\Fix{cite}, and Microsoft's Chakra\Fix{cite}) need to
follow the constant changes in the language
specification~\cite{kangax}. Recently, the JavaScript
specification went through a bigger change compared to prior
releases\footnote{Called by the name of ECMAScript6
  (ES6)~\cite{es6-features}}. As in any piece of software, changes in
the specification often demand sensible changes in implementations
that could lead to errors, including regressions. In fact, bugs in JS
implementations are often reported by the general public, some of
which were reported by our team.
